---
title: "data_viz_eod"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## 
```{r}
library(tidyverse)
library(here)
library(lubridate)

space <- read_csv(here("data", "space_launches.csv"))

```

```{r}
p <- ggplot(data = space, aes(x = launch_year, y = type))+
  geom_crossbar(xmin = 1957, xmax = 2018)
```````

```{r}
p +
  theme(panel.grid.major = element_line(color = "pink"),
  plot.background = element_rect(fill = "cyan"),
  text = element_text(size = 22, family = "mono"),
  axis.text.x = element_text(color = "purple"),
  axis.text.y = element_text(color = "green"),
  panel.background = element_rect(color = "black", fill = "yellow"))+
  labs(x = "figure it out, bro", y = "can't u read")

ggsave(here("figs", "mybadfig.png"))
  
```

# Task 2
```{r}
sf_ghg <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))
```````

```{r}
sf_sector <- sf_ghg %>%
  select(Emissions_mtCO2e, Sector_General)%>%
  group_by(Sector_General)%>%
  summarize(total_ghg = sum(Emissions_mtCO2e, na.rm = TRUE))
```

```{r}
sf_commodity_year <- sf_ghg %>%
  select(Calendar_Year, Commodity_Type, Emissions_mtCO2e)%>%
  group_by(Calendar_Year, Commodity_Type) %>%
  summarize(Emissions_mtCO2e = sum(Emissions_mtCO2e, na.rm = TRUE))
  
```

```{r}
sf_subset <- sf_ghg %>%
  filter(Calendar_Year >= 2005) %>%
  filter(str_detect(Sector_Detail2,"PG&E")) %>%
  select(Calendar_Year, Commodity_Type, Emissions_mtCO2e)
  
```

Task 3
```{r}
ggplot(data = sf_ghg, aes(x= Calendar_Year, y = Emissions_mtCO2e)) +
  geom_point(aes(color = Sector_General))

```

